dynamics

### 2023-03-01 scripts/workshop/dynamics.Rmd
fix some errors and knit

Neutral
```{r}
params_n <- c(mu_a=1/50,
          mu_b=1/50,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

>>>>

Neutral
```{r}
params_n <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters
